TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-23 paper/paper.tex
Minor change in wording
Minor wording change

BBR is the best-performing algorithm in our set, because it barely responds to
packet loss. However, we were unable to reproduce the results written in the paper by Mario Hock et al \cite{bbr-congestion-comparison}. We used multiple values to simulate packet loss as well as delay, which simulate having small buffers. BBR is a TCP congestion control protocol that reacts to the minimum RTT in combination with the Bottleneck Bandwidth. We have tested multiple delay values that appear in the real world. The delay values are directly related to the minimum RTT possible on the link. As mentioned in the results, we see no hard evidence that this
causes other algorithms to reduce their speed further, but there are slight
indications. For example in the test of DCTCP versus BBR, DCTCP reaches around
0.2 to 0.6 megabytes per second. In the test of DCTCP versus BIC, this is 0.3
to 0.7 megabytes per second. The difference is large nor statistically
significant, but it warrants looking into. On the scale of 0.7 megabytes per
second, a tenth of a megabyte does make a difference.

@@

For the algorithms BIC, BBR, CUBIC and DCTCP, we conclude that they allocate
bandwidth fairly and do not suppress each other. There is no impact on the
service for customers when using those algorithms mixed in one environment.

>>>>

BBR is the best-performing algorithm in our set, because it barely responds to
packet loss. However, we were unable to draw the same conclusions to our results as the conclusions written in the paper by Mario Hock et al \cite{bbr-congestion-comparison}. We used multiple values to simulate packet loss as well as delay, which simulate having small buffers. BBR is a TCP congestion control protocol that reacts to the minimum RTT in combination with the Bottleneck Bandwidth. We have tested multiple delay values that appear in the real world. The delay values are directly related to the minimum RTT possible on the link. As mentioned in the results, we see no hard evidence that this
causes other algorithms to reduce their speed further, but there are slight
indications. For example in the test of DCTCP versus BBR, DCTCP reaches around
0.2 to 0.6 megabytes per second. In the test of DCTCP versus BIC, this is 0.3
to 0.7 megabytes per second. The difference is large nor statistically
significant, but it warrants looking into. On the scale of 0.7 megabytes per
second, a tenth of a megabyte does make a difference.

@@

For the algorithms BIC, BBR, CUBIC and DCTCP, we conclude that, based on the setup we have used, they allocate
bandwidth fairly and do not suppress each other. There is no impact on the
service for customers when using those algorithms mixed in one environment.
